# r document van Steensel lab

# Gene repression in LADs
## Christ Leemans, 22-08-2018

## Introduction
We have performed TRIP with 3 escapers and 3 repressed promoters.
To test relative expression of the TRIP constructs before integration, Marloes
measured RNA expression from transfected plasmids.

First she mixed the 6 promoters in different ratio's (1:1:1:1:1:1 and 1:2:1:2:1:2).
Unfortunately there was a mix up of samples however, so in the end 1 replicate of
each ratio was found to be correctly labeled.

Because of this and because we wanted to add the hPGK which we used as a reference
for a promoter which is really insensitive to chromatin context.

Unfortunately the first time this was attempted, the plasmids didn't contain any
promoter. The second try however was successful. But although within each promoter
there was a very narrow distribution, like previous analysis, some promoters have
shifted in the expression that was predicted from this experiment compared to
previous experiments.

Although this is very unfortunate, it does not hinder the conclusions that we
would like to draw from this date, namely that:
1 ) the escaper promoters do not escape simply because they are more active
2 ) the range of expression observed in the TRIP pools can not be explained by
    barcode effects.

## individual plasmid PCR's

plasmids from each promoter were sequenced separately to link each barcode to
a promoter
```{r}
library(ggbeeswarm)
library(ggplot2)
library(reshape2)
library(plyr)
library(rtracklayer)
library(subSeq)
library(data.table)
library(grid)

COLi<-"#00BBFF11" #dot color for iLAD promoters
COL_lad<-c("#FF0000", "#0077FF")
names(COL_lad)<-c('LAD', 'iLAD')

#color vector for plotting:
COL_class<-c("#A020F0", "#FFA500", "#006400", "#7e7e7e", "#0077FF")
names(COL_class)<-c("repressed", "escaper", "inactive", 'boundary', 'iLAD')


single_files = list.files('../../trip/cl20180813_TRIP_transient_mix/gDNA',
                          pattern='^[0-9hPGK]+_.*.starcode.count', full.names=T)
names(single_files) = gsub('.*gDNA/(.*).starcode.count', '\\1', single_files)

single_info = data.frame(row.names=names(single_files),
                         promoter=gsub('(.+?)_.*', '\\1', names(single_files)),
                         rep = gsub('.+?_A_r([0-9]).*', '\\1', names(single_files)),
                         stringsAsFactors=F)


single_table_list = lapply(names(single_files), function(name){
        df = read.table(single_files[name], stringsAsFactors=F, fill=T)
        return(data.frame(barcode=df[,1],
                          starcount=df[,2],
                          promoter=single_info[name,'promoter'],
                          rep = single_info[name,'rep'],
                          stringsAsFactors=F))
    })

prom_name = c('6'='ADAMTS1', '8'='TMEM106B', '9'='MED30', '11'='ARHGEF9',
              '12'='ZNF300', '10'='BRINP1', 'hPGK'='hPGK')
class_vec = c('6'='repressed', '8'='escaper', '9'='escaper', '11'='repressed',
              '12'='escaper', '10'='repressed', 'hPGK'='iLAD')

single_list = lapply(unique(single_info$promoter), function(prom){
    i_vec = which(single_info$promoter==prom)
    this_list = single_table_list[i_vec]
    rep1 = this_list[[1]]
    rep2 = this_list[[2]]
    bc_1 = rep1$barcode[rep1$starcount > 100]
    bc_2 = rep2$barcode[rep2$starcount > 100]
    bc_vec = bc_1[bc_1%in%bc_2]
    data.frame(row.names= bc_vec,
               promoter = rep(prom, length(bc_vec)),
               prom_name = prom_name[prom],
               class = class_vec[prom],
               stringsAsFactors=F)
})

single_table = do.call(rbind, single_list)


```


```{r}


parse_norm_files <- function(norm_files){
    names(norm_files) = gsub('.*cDNA/(.*).normalized', '\\1', norm_files)


    norm_info = data.frame(row.names=names(norm_files),
                           mix=gsub('(.+?)_.*', '\\1', names(norm_files)),
                           bio_rep = gsub('.+?_(.+?)_.*', '\\1', names(norm_files)),
                           tech_rep = gsub('.+?_.+?_r([^.]*).*', '\\1', names(norm_files)),
                           stringsAsFactors=F)
    norm_table_list = lapply(norm_files, read.table, row.names=1, header=T,
                             stringsAsFactors=F)
    names(norm_table_list) = names(norm_files)

    norm_list = lapply(unique(norm_info$mix), function(mix){
        this_info = norm_info[norm_info$mix==mix, ]
        bio_list = lapply(unique(this_info$bio), function(bio){
            name_vec = rownames(this_info)[this_info$bio==bio]
            rep1 = norm_table_list[[name_vec[1]]]
            rep2 = norm_table_list[[name_vec[2]]]
            bc1 = rownames(rep1)
            bc2 = rownames(rep2)
            bc_vec = bc1[bc1%in%bc2]

            colnames(rep1) = paste0(colnames(rep1), '_1')
            colnames(rep2) = paste0(colnames(rep2), '_2')

            rep_df = data.frame(barcode=bc_vec,
                                rep1[bc_vec, ],
                                rep2[bc_vec, ],
                                mix=mix,
                                bio=bio,
                                single_table[bc_vec, ],
                                stringsAsFactors=F)
            print(ggplot(rep_df, aes(x=log2(normalized_by_gDNA_1),
                                     y=log2(normalized_by_gDNA_2))) +
                   geom_point(alpha=0.5))
            rep_df$norm = rowMeans(rep_df[,c('normalized_by_gDNA_1',
                                             'normalized_by_gDNA_2')])
            return(rep_df)
        })
        do.call(rbind, bio_list)
    })
    norm_data = do.call(rbind, norm_list)
    return(norm_data)
}


dir_vec = c('../../trip/cl20180501_TRIP_transient_mix/cDNA',
            '../../trip/cl20180704_TRIP_mixpool/cDNA',
            '../../trip/cl20180813_TRIP_transient_mix/cDNA')

norm_list = lapply(1:length(dir_vec), function(i){
    norm_files = list.files(dir_vec[i], pattern='normalized', full.names=T)
    if (i==2){
        norm_files = grep('plasmid', norm_files, value=T)
    }
    norm_data = parse_norm_files(norm_files)
    norm_data$attempt = c('A','B','C', 'D')[i]
    return(norm_data)
})


esc_repr_list = lapply(norm_list, function(norm){
    norm = norm[which(norm$class%in%c('escaper', 'repressed')),]
    ddply(norm, .(bio), function(bio_norm){
        col_sum = colSums(bio_norm[,grep('count', colnames(bio_norm))])
        bio_norm[,c('cDNA_cpm_1', 'gDNA_cpm_1')] =
            t(t(bio_norm[,c('cDNA_count_1', 'gDNA_count_1')]) /
              col_sum[1:2] * min(col_sum[1:2]))
        bio_norm$norm_1 = bio_norm$cDNA_cpm_1 / bio_norm$gDNA_cpm_1


        bio_norm[,c('cDNA_cpm_2', 'gDNA_cpm_2')] =
            t(t(bio_norm[,c('cDNA_count_2', 'gDNA_count_2')]) /
              col_sum[3:4] * min(col_sum[3:4]))
        bio_norm$norm_2 = bio_norm$cDNA_cpm_2 / bio_norm$gDNA_cpm_2

        bio_norm$norm = rowMeans(bio_norm[, c('norm_1', 'norm_2')])
        return(bio_norm)
    })
})

esc_repr_data = do.call(rbind, esc_repr_list)

esc_repr_cast = dcast(esc_repr_data, prom_name + class + barcode ~ attempt + bio,
                      value.var='norm')
col_name_vec = colnames(esc_repr_cast)[4:ncol(esc_repr_cast)]
## remove A_B and A_C since these samples seem to have been mixed up.
col_name_vec = col_name_vec[!col_name_vec %in% c('A_B', 'A_C') ]

esc_repr_cast$mean = rowMeans(esc_repr_cast[,col_name_vec])

pdf('cl20180828_mean_plasmid_mix_esc_repr.pdf', useDingbats=F)
ggplot(esc_repr_cast, aes(x=prom_name, y=mean, color=class)) +
    geom_quasirandom(size=0.4) +
    geom_boxplot(alpha=0, color='black') +
    scale_color_manual(values=COL_class)
dev.off()


pgk_data = norm_list[[3]][which(norm_list[[3]]$prom_name=='hPGK'), ]
pgk_norm = ddply(pgk_data, .(bio), function(bio_norm){
    col_sum = colSums(bio_norm[,grep('count', colnames(bio_norm))])
    bio_norm[,c('cDNA_cpm_1', 'gDNA_cpm_1')] =
        t(t(bio_norm[,c('cDNA_count_1', 'gDNA_count_1')]) /
          col_sum[1:2] * min(col_sum[1:2]))
    bio_norm$norm_1 = bio_norm$cDNA_cpm_1 / bio_norm$gDNA_cpm_1


    bio_norm[,c('cDNA_cpm_2', 'gDNA_cpm_2')] =
        t(t(bio_norm[,c('cDNA_count_2', 'gDNA_count_2')]) /
          col_sum[3:4] * min(col_sum[3:4]))
    bio_norm$norm_2 = bio_norm$cDNA_cpm_2 / bio_norm$gDNA_cpm_2

    bio_norm$norm = rowMeans(bio_norm[, c('norm_1', 'norm_2')])
    return(bio_norm)
})


pgk_cast = dcast(pgk_norm, prom_name + class + barcode ~ attempt + bio,
                 value.var='norm')

pgk_cast$mean = rowMeans(pgk_cast[,c('C_A', 'C_B')])




offset_data = norm_list[[3]][!is.na(norm_list[[3]]$class), ]

offset_data$is_pgk = offset_data$prom_name=='hPGK'

offset_count = ddply(offset_data, .(is_pgk, bio), function(x){
    colSums(x[,grep('count', colnames(x))])
})

offset_norm = ddply(offset_count, .(bio), function(x){
    col_sum = colSums(x[,grep('count', colnames(x))])
    cpm_1 = t(t(x[,c('cDNA_count_1', 'gDNA_count_1')]) /
              col_sum[1:2] * min(col_sum[1:2]))
    colnames(cpm_1) = c('cDNA_cpm_1', 'gDNA_cpm_1')
    norm_1 = cpm_1[,1] / cpm_1[,2]

    cpm_2 = t(t(x[,c('cDNA_count_2', 'gDNA_count_2')]) /
              col_sum[1:2] * min(col_sum[1:2]))
    colnames(cpm_2) = c('cDNA_cpm_2', 'gDNA_cpm_2')
    norm_2 = cpm_2[,1] / cpm_2[,2]
    return(data.frame(x, cpm_1, cpm_2, norm_1, norm_2))
})

offset_norm$norm = rowMeans(offset_norm[,c('norm_1', 'norm_2')])

offset_cast = dcast(offset_norm, is_pgk ~ bio, value.var='norm')
offset_cast$mean = rowMeans(offset_cast[,c('A', 'B')])

pgk_cast$mean_offset = pgk_cast$mean * offset_cast[offset_cast$is_pgk, 'mean']
esc_repr_cast$mean_offset = esc_repr_cast$mean * offset_cast[!offset_cast$is_pgk, 'mean']


mean_offset = rbind(pgk_cast[,c('prom_name', 'class', 'barcode', 'mean_offset')],
                    esc_repr_cast[,c('prom_name', 'class', 'barcode', 'mean_offset')])


pdf('cl20180904_plasmid_mix_expression.pdf', useDingbats=F, width=5, height=5)

ggplot(mean_offset, aes(x=log2(mean_offset), y=promoter, color=class)) +
    geom_quasirandom(alpha=0.5, size=0.5, groupOnX=FALSE) +
    theme_bw() +
    scale_color_manual(values=COL_class) +
    stat_summary(fun.y = median, fun.ymin = median, fun.ymax = median,
                 geom = "crossbar", color='black', width = 0.4) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    xlab('log2(expression)') +
    ylab('promoter') +
    guides(color=FALSE)
dev.off()

sd_table_plasmid = aggregate(log2(mean_offset) ~ prom_name, sd, data=mean_offset )

mean(sd_table_plasmid[,2])
sd(sd_table_plasmid[,2])


```



```{r}


rev_file_list = list.files('../../trip/cl20180409_TRIP_K562_evsr/mapping',
                           pattern='2.table', full.names=T)
names(rev_file_list) = gsub('.*mapping/(.*).2.table', '\\1', rev_file_list)

map_info = data.frame(name=names(rev_file_list),
                      promoter=gsub('(.+?)_.*', '\\1', names(rev_file_list)),
                      bio_rep = gsub('.+?_(.+)_.*', '\\1', names(rev_file_list)),
                      tech_rep = gsub('.+?_.+?_r([0-9])', '\\1', names(rev_file_list)),
                      stringsAsFactors=F)


rev_table_list = lapply(rev_file_list, read.table, header=T, stringsAsFactors=F,
                        row.names=1)

call_file_list = list.files('../../trip/cl20180409_TRIP_K562_evsr/calls',
                            full.names=T)
names(call_file_list) = gsub('.*calls/(.*).txt', '\\1', call_file_list)

call_info = data.frame(name=names(call_file_list),
                       promoter=gsub('(.+?)_.*', '\\1', names(call_file_list)),
                       bio_rep = gsub('.+?_(.+)_.*', '\\1', names(call_file_list)),
                       call = gsub('.+?_.+?_(.+)', '\\1', names(call_file_list)),
                       stringsAsFactors=F)


dam_file_list = list.files('../../trip/cl20180409_TRIP_K562_evsr/dam',
                             pattern='.txt', full.names=T)
names(dam_file_list) = gsub('.*dam/(.*).txt', '\\1', dam_file_list)

dam_info = data.frame(name=names(dam_file_list),
                      promoter=gsub('(.+?)_.*', '\\1', names(dam_file_list)),
                      bio_rep = gsub('.+?_(.+?)_.*', '\\1', names(dam_file_list)),
                      target = gsub('.+?_.+?_(.+?)_.*', '\\1', names(dam_file_list)),
                      window = gsub('.+?_.+?_.+?_(.*)', '\\1', names(dam_file_list)),
                      stringsAsFactors=F)

dam_table_list = lapply(dam_file_list, read.table, header=T, row.names=1,
                       stringsAsFactors=F)
names(dam_table_list) = dam_info$name


call_table_list = lapply(call_file_list, read.table, header=T, row.names=1)



chip_domain_file_list = list.files('../../trip/cl20180409_TRIP_K562_evsr/chip/domains_call',
                            pattern='.txt', full.names=T)
names(chip_domain_file_list) = gsub('.*call/(.*).txt', '\\1', chip_domain_file_list)

chip_domain_info = data.frame(name=names(chip_domain_file_list),
                              promoter=gsub('(.+?)_.*', '\\1', names(chip_domain_file_list)),
                              bio_rep = gsub('.+?_(.+?)_.*', '\\1', names(chip_domain_file_list)),
                              experiment = gsub('.+?_.+?_(.+?)_.*', '\\1',
                                             names(chip_domain_file_list)),
                               target = gsub('.+?_.+?_.+?_(.+?)_.*', '\\1',
                                                 names(chip_domain_file_list)),
                               sample = gsub('.+?_.+?_.+?_.+?_(.+?)', '\\1',
                                             names(chip_domain_file_list)),
                               stringsAsFactors=F)

chip_domain_table_list = lapply(chip_domain_file_list, read.table, header=F,
                               stringsAsFactors=F, row.names=4,
                               col.names=c('seqnames', 'start', 'end', 'barcode',
                                           'score', 'strand', 'call'))



class_vec = c('6'='repressed', '8'='escaper', '9'='escaper', '11'='repressed',
              '12'='escaper', '10'='repressed', 'hPGK'='iLAD')
COL_vec = c(repressed="#A020F0", escaper="#FFA500", iLAD="#0077FF")

mapping_list = lapply(names(class_vec), function(prom){
    bio_list = lapply(unique(map_info$bio_rep), function(bio){
        name_vec = map_info[map_info$promoter==prom & map_info$bio==bio, 'name']
        rep_vec = map_info[map_info$promoter==prom & map_info$bio==bio, 'tech_rep']
        name = name_vec[rep_vec=="1"]
        rev_data = rev_table_list[name_vec]
        rep1 = rev_data[[which(rep_vec=="1")]]
        rep2 = rev_data[[which(rep_vec=="2")]]
        rep1$ratio1 = rep1$reads1 / rep1$total_mapped
        rep1$ratio2 = rep1$reads2 / rep1$total_mapped
        rep1$avg_mapq = rep1$mapq_sum1 / rep1$reads1

        rep2$ratio1 = rep2$reads1 / rep2$total_mapped
        rep2$ratio2 = rep2$reads2 / rep2$total_mapped
        rep2$avg_mapq = rep2$mapq_sum1 / rep2$reads1

        rep1$unique = rep1$ratio1 > 0.7 & rep1$ratio2 < 0.1 & rep1$avg_mapq > 10 &
                   rep1$reads1 > 5
        rep2$unique = rep2$ratio1 > 0.7 & rep2$ratio2 < 0.1 & rep2$avg_mapq > 10 &
                   rep2$reads2 > 5

        ## which barcodes were in found in both replicates
        shared_bc = rownames(rep1)[rep1$unique][rownames(rep1)[rep1$unique] %in%
                                                rownames(rep2)[rep2$unique]]
        ## do they map to the same location?
        equal = rep1[shared_bc, c('seqname', 'ori', 'start_pos')] ==
                 rep2[shared_bc, c('seqname', 'ori', 'start_pos')]
        not_equal = shared_bc[which(rowSums(equal) != 3)]
        unique_rep1 = rownames(rep1)[rep1$unique][!(rownames(rep1)[rep1$unique] %in%
                                                  rownames(rep2)[rep2$unique])]
        unique_rep2 = rownames(rep2)[rep2$unique][!(rownames(rep2)[rep2$unique] %in%
                                                  rownames(rep1)[rep1$unique])]
        shared_bc = rownames(rep1)[rownames(rep1) %in%
                              rownames(rep2)]
        shared_bc = shared_bc[!shared_bc %in% not_equal]
        equal = rep1[shared_bc, c('seqname', 'ori', 'start_pos')] ==
               rep2[shared_bc, c('seqname', 'ori', 'start_pos')]
        equal_bc = shared_bc[which(rowSums(equal) == 3)]
        map_data = rep1[equal_bc, ]
        map_data[, c('total_mapped', 'mapq_sum1',
            'reads1', 'mapq_sum2', 'reads2')] =
            rep1[equal_bc, c('total_mapped', 'mapq_sum1',
                             'reads1', 'mapq_sum2', 'reads2')] +
            rep2[equal_bc, c('total_mapped', 'mapq_sum1',
                             'reads1', 'mapq_sum2', 'reads2')]
        not_equal_bc = shared_bc[which(rowSums(equal) != 3)]
        map_data = rbind(map_data,
                         rep1[not_equal_bc[rep1[not_equal_bc, 'unique']], ],
                         rep2[not_equal_bc[rep2[not_equal_bc, 'unique']], ])
        map_data = rbind(map_data,
                          rep1[!rownames(rep1) %in% rownames(rep2), ],
                          rep2[!rownames(rep2) %in% rownames(rep1), ])
        this_call = call_info[call_info$promoter==prom & call_info$bio_rep==bio,]
        cl_df = do.call(cbind, call_table_list[this_call$name])
        colnames(cl_df) = gsub(paste0(prom, '_', bio, '_'), '', colnames(cl_df))


        this_dam = dam_info[dam_info$promoter==prom &
                                  dam_info$bio_rep==bio,]
        dl = lapply(dam_table_list[this_dam$name],
                    function(x){return(x[,'mean', drop=F])})
        dl_df = do.call(cbind, dl)
        colnames(dl_df) = paste0(this_dam$target, '_DamID')

        this_chip_domain = chip_domain_info[chip_domain_info$promoter==prom &
                                            chip_domain_info$bio_rep==bio,]
        cd = lapply(chip_domain_table_list[this_chip_domain$name],
                    function(x){return(x[,'call', drop=F])})
        cd_df = do.call(cbind, cd)
        colnames(cd_df) = paste(this_chip_domain$experiment, this_chip_domain$target,
                                this_chip_domain$sample, 'call', sep='_')

        df = data.frame(map_data[,c('seqname', 'ori', 'start_pos', 'unique')],
                        cl_df[rownames(map_data), ],
                        dl_df[rownames(map_data), ],
                        cd_df[rownames(map_data), ],
                        prom=prom,
                        bio=bio)
        df$lad = ifelse(is.na(df$LMNB1.domain_index) , 'iLAD', 'LAD')
        return(df)
    })
    names(bio_list) = unique(map_info$bio_rep)
    return(bio_list)
})
names(mapping_list) = names(class_vec)


check_reproducability <- function(rep1, rep2){
    bc_vec1 = rownames(rep1)
    bc_vec2 = rownames(rep2)
    bc_vec = bc_vec1[bc_vec1 %in% bc_vec2]
    uniq_rep1 = bc_vec1[!bc_vec1 %in% bc_vec2]
    uniq_rep2 = bc_vec2[!bc_vec2 %in% bc_vec1]
    cat(paste0('shared: ', length(bc_vec), '\n'))
    cat(paste0('rep1 unique: ', length(uniq_rep1), '\n'))
    cat(paste0('rep2 unique: ', length(uniq_rep2), '\n'))
    bc_vec = bc_vec[rep1[bc_vec, 'gDNA_count'] > 100 | rep2[bc_vec, 'gDNA_count'] > 100]
    cat(paste0('above threshold (> 100 gDNA either rep): ', length(bc_vec), '\n'))
    cat(paste0('rep1 unique > 100: ', length(which(rep1[uniq_rep1, 'gDNA_count'] > 100)),
               '\n'))
    cat(paste0('rep2 unique > 100: ', length(which(rep2[uniq_rep2, 'gDNA_count'] > 100)),
               '\n'))
    colnames(rep1) = paste0(colnames(rep1), '_1')
    colnames(rep2) = paste0(colnames(rep2), '_2')
    norm_data = data.frame(rep1[bc_vec, ], rep2[bc_vec, ],
                           barcode=bc_vec, stringsAsFactors=F)
    norm_data$norm = rowMeans(norm_data[,c('normalized_by_gDNA_1',
                                           'normalized_by_gDNA_2')])
    return(norm_data)
}



exp_file_list = list.files('../../trip/cl20180409_TRIP_K562_evsr/cDNA', pattern='normalized',
                       full.names=T)
names(exp_file_list) = gsub('.*cDNA/(.*).normalized', '\\1', exp_file_list)

exp_table_list = lapply(exp_file_list, read.table, header=T, stringsAsFactors=F,
                        row.names=1)

exp_info = data.frame(name=names(exp_file_list),
                      promoter=gsub('([0-9]+).*', '\\1', names(exp_file_list)),
                      bio_rep = gsub('[0-9]+([A-B]).*', '\\1', names(exp_file_list)),
                      tech_rep = gsub('[0-9]+[A-B]_r(.*)', '\\1', names(exp_file_list)),
                      stringsAsFactors=F)
exp_info$promoter = gsub('(.*)_.*_.*', '\\1', exp_info$promoter)
exp_info$bio_rep = gsub('.*_(.*)_.*', '\\1', exp_info$bio_rep)
exp_info$tech_rep = gsub('.*_.*_r(.*)', '\\1', exp_info$tech_rep)

exp_list = lapply(unique(exp_info$promoter), function(prom){
    lapply(unique(exp_info$bio_rep), function(bio){
        name_vec = exp_info[exp_info$promoter==prom & exp_info$bio==bio, 'name']
        rep1 = exp_table_list[[name_vec[1]]]
        rep2 = exp_table_list[[name_vec[2]]]
        norm_data = check_reproducability(rep1, rep2)
        map_data = mapping_list[[prom]][[bio]]
        data.frame(norm_data, prom=prom, bio=bio,
                   map_data[norm_data$barcode, ],
                   stringsAsFactors=F)
    })
})
exp_df = do.call(rbind, lapply(exp_list, function(l){do.call(rbind,l)}))
prom_name = c('6'='ADAMTS1', '8'='TMEM106B', '9'='MED30', '11'='ARHGEF9',
              '12'='ZNF300', '10'='BRINP1', 'hPGK'='hPGK')
exp_df$prom_name = prom_name[exp_df$prom]
exp_df$class = class_vec[exp_df$prom]

bc_table = table(exp_df$barcode)
bc_vec = names(bc_table)[bc_table==1]

exp_df = exp_df[which(exp_df$barcode%in%bc_vec), ]


trip_data = exp_df[which(exp_df$lad %in% c('iLAD', 'LAD') & exp_df$unique &
                         exp_df$seqname!='chrY'), ]

sd_table_pool = aggregate(log2(norm) ~ prom_name, sd, data=trip_data)
mean(sd_table_pool[,2])
sd(sd_table_pool[,2])

t.test(sd_table_plasmid[,2], sd_table_pool[,2])

```
